\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

\title{Index for Notes}
\author{Tom Augspurger}
\date{\today}
\begin{document}
\fontsize{8}{.5}\selectfont

% Need item, group(s), page.

\section{Intro}
\label{sec:intro}
\begin{itemize}
    \item T 0.1.3: Bolzano-Weirstrauss. p. 0.3
\end{itemize}

\section{Unconstrained Optimization}
\label{sec:unconstrained_optimization}
\subsection{Univariate}
\label{sub:univariate}
  \begin{itemize}
    \item T I.2.1.1: UnivariateFirst-order necessary. p. I.1
    \item T I.2.1.3: UnivariateSecond-order necessary. p. I.1
    \item T I.2.1.4: UnivariateSecond-order suffiecent. p. I.2
  \end{itemize}

\subsection{Multivariate}
\label{sub:multivariate}
  \begin{itemize}
    \item T I.2.2.1: Multivariate First-order necessary. p. I.2
    \item L I.2.2.3: saddle point. p. I.3
    \item L I.2.2.5: symmetric positive definite. p.1.3
    \item T I.2.2.6: Multivariate Second-order necessary. p. I.3
    \item T I.2.2.7: Multivariate Second-order suffiecent. p. I.4
    \item L I.2.2.9: Dir of Decrease. p. I.5
    \item C I.2.2.12: Local min $\Rightarrow \nexists$ des. dir. p. I.6
    \item L I.2.2.14: p.I.6
  \end{itemize}

\subsection{Quadratic}
\label{sub:quadratic}
  \begin{itemize}
    \item L I.2.3.1: Conditions on H for min/max/saddle. p. I.8
    \item C I.2.3.2: $x^*$ global min, gradient = 0, H is psd. p. I.9
    \item A I.3.1.5: Interval reduction. p. I.10.
  \end{itemize}

\subsection{Minimizing algorithms for univariate obj. functions.}
\label{sub:minimizing_algorithms_for_univariate_obj_functions}

  pass

\subsection{Minimizing algorithms for multivariate obj. functions.}
\label{sub:minimizing_algorithms_for_multivariate_obj_functions}

\begin{itemize}
  \item E I.4.1.1 Quadratic subproblem. p. I.15
  \item E I.4.1.2: Search Direction $H_k p_k = -c_k$. p. I.15
  \item E I.4.1.4: Steepest Descent. p. I.15
\end{itemize}

\subsection{Polynomial Interpolation}
\label{sub:polynomial_interpolation}

\subsection{I.4.2: Quasi-Newton Methods}
\label{sub:quasi_newton_methods}
  \begin{itemize}
    \item I.4.2.1: \textbf{Quasi-Newton Condition} $B_+ s = y$. p. I.21
    \item NA: SR1 update. p. I.22
    \item I.4.2.4: BFGS Update. p. I.23
    \item I.4.2.7: DFP Update. p. I.24
    \item I.4.2.8: Broyden \emph{Class} of Updates. p. I.24
    \item L I.4.2.4: Quadratic unique min. p. I.25
    \item A I.4.2.5: BFGS On quad w/ els. p. I.25
    \item T I.4.2.6: \^ properties, like CDM. p. I.26
  \end{itemize}

\subsection{The Linear and Nonlinear CG Methods}
\label{sub:the_linear_and_nonlinear_cg_methods}

\begin{itemize}
  \item A I.4.3.2 CD Method. p. I.28
  \item A I.4.3.4 CG Method. p. I.30
  \item T I.4.3.5 Properties of CG. p. I.31
\end{itemize}

\section{Nonlinear Equations}
\label{sec:nonlinear_equations}

\subsection{Sufficent Conditions}
\label{sub:sufficent_conditions}
  \begin{itemize}
    \item T II.2.1.2: CMT: p. II.2
  \end{itemize}
% Typed Stuff

\subsection{Multivariate Nonlinear Equations}
\label{sec:multivariate_nonlinear_equations}

  \begin{itemize}
    \item T II.2.2.1: Inverse Function Thrm. p. II.2
    \item T II.2.2.2: Contraction Mapping. p. II.3
    \item T II.2.2.3: Suff. for CM. p. II.4
  \end{itemize}

\subsection{Zero Finding Algorithms For Univariate Nonlinear Functions}
\label{sub:zero_finding_algorithms_for_univariate_nonlinear_functions}

  \subsubsection{Interval Reduction Methods}
  \label{subsub:interval_reduction_methods}

    \begin{itemize}
      \item A II.3.1.3: Bisection Algorithm. p. II.6
    \end{itemize}

  \subsubsection{Newton's Method}
  \label{subsub:newton_s_method}
    \begin{itemize}
      \item E II.3.2.1: $L_k^N(x) = F(X_k) + F'(x_K)(x = x_k)$. p. II.8
    \end{itemize}

\subsection{Zero Finding Algorithms For Multivariate Nonlinear Functions}
\label{sub:zero_finding_algorithms_for_multivariate_nonlinear_functions}

  \subsubsection{Newton's Method}
  \label{subsub:newton_s_method}
  \begin{itemize}
    \item E II.4.1.0: same
    \item L II.4.1.1: Newton iterates. p. II.14
  \end{itemize}

  \subsubsection{Quasi-Newton Methods}
  \label{subsub:quasi_newton_methods}

  \begin{itemize}
    \item E II.4.3.1: Quasi-Newton Equation. $B_{k+1}s_k = y_k$ p. II.18
    \item E II.4.3.3: Good Broyden Update. p. II.19
  \end{itemize}
\section{Conjugate Gradient Method}
\label{sec:conjugate_gradient_method}
\subsection{Typed}
\label{sub:typed}
  \begin{itemize}
    \item T 3.13: min / nonlinear eq same. p.71
    \item L 3.14: quadratic direction. p.71
    \item A 3.5.1: Conjugate Direction Method. p.72
    \item L 3.17: Min affine subspace. p.72
    \item A 3.5.2 Conjugate Gradient Method. p.74
    \item T 3.19: Properties of \^. p.74
    \item note: $p_{k+1} \equiv -g_{k+1} + B_k p_k$, $g_k \equiv \nabla q(x_k) = H x_k - b$
  \end{itemize}

\section{Typed Solving Univariate Nonlinear Equations}
\label{sub:typed solving univariate nonlinear equations}

\subsection{Bisection Method}
\label{sub:bisection_method}
  \begin{itemize}
    \item A 7.1.1 Bisection method p. 106
    \item T 7.1 Global Convergecne of \^. p. 106
  \end{itemize}
\subsection{Neton's Method \& Modified}
\label{sub:neton_s_method}
  \begin{itemize}
    \item A 7.21: Newton's  method p. 108
    \item E 7.3.1: Modified newton method. p. 109
  \end{itemize}
\subsection{Fixed Point}
\label{sub:fixed_point}
  \begin{itemize}
    \item D 7.4.1: Definition. p. 111
    \item T 7.5: CMT. p. 112
  \end{itemize}
  \end{document}
